\subsection{Component}
\label{subsec:detailed_component}
The component is a simple base class that all components must inherit from.
It is our solution to the problem of writing generic code without knowing different component
types through templates.
\todo{Explain what we are solving. Done?}

\subsubsection{Explanation}
The component exists to ensure that all components get a minimum set of needed
variables, like an entity id and a reference to the entity manager.
The component also fills the role of being a general interface
internally within the ECS, as the ECS does not directly see component types,
but just raw memory that is reinterpreted as component pointers.
It is the component pointers together with the meta information\secref{subsec:detailed_meta_information},
that allows for the generic behavior without direct type information.

\subsubsection{Motivation}
As with a lot of the building block structures within the ECS. The need for a base component
were motivated out of the requirement for avoiding heavy template usage\reqref{req:templates}.
The ECS would need a way to extract certain information related to components,
like their id. The component could potentially need access to the entity manager\secref{subsec:detailed_entity_manager}
to get a hold of other components, so making that a reference
would ensure that all components would have access to it.

\subsubsection{Alternatives}
Certain alternatives could be have been pursued instead of the base class model.

\paragraph{ID Component Pairs}
One approach could be to keep components and id's as separate objects, and store them in a pair structure.
This would mean that a component would potentially avoid unneeded members like the entity manager pointer.
It would also lead to even less coupling within the systems,
as the components would not need to inherit from the component base class.
However, going with this approach would require even more opaque type usage within the ECS,
and more reinterpret casting for the user.
Obviously this solution would become more relevant if the template requirement was lifted.

\todo{More alternatives?}

\subsubsection{Pros}
The main advantage of the component base class over the alternatives of the component pair is that it allows
for a use of the component base class as an interface.
Additionally, inheriting from a base class allows for declaration of all member functions that is used within the ECS,
which is used with the operation types\secref{subsec:detailed_operation_types} to discover overloads of member functions.

\subsubsection{Cons}
One of the main disadvantages of the component base class is that it couples the components to the system.
