\documentclass{article}

\begin{document}

\begin{center}
\subsection*{Supervisor meeting 08.03.2017}
\subsubsection*{With: Mariusz Nowostawski}
\end{center}

\bigskip


\subsubsection*{Intention of the meeting}
Update on progress.


\subsubsection*{Questions to the supervisor}
\begin{itemize}
    \item 
    Ok to just test on ubuntu?
    
    \item 
    Feedback on design?
\end{itemize}


\subsubsection*{Answers to our questions}
\begin{itemize}
    \item 
    If it is cleared with Suttung it is ok. 
    We will still use more compilers.
    
    \item 
    Design seems good.
\end{itemize}


\subsubsection*{New tasks from our supervisor}
\begin{itemize}
    \item \textbf{Isolate optimizations}\\
    See if we can test all optimization in isolation, so we can demonstrate that the different optimizations are worth it on their own.

    \item \textbf{Virtuals test}\\
    Do one test with virtuals instead of function pointers.

    \item \textbf{Lookup strategies}\\
    Think about different strategies for looking up components. 
    \begin{itemize}
        \item
        Lookup table/Big array.

        \item
        Hash table.

        \item
        Index Map.\\
        Have a outer array outside of the collection that is sorted and has pointer into the collection.\\
        The outer array is sorted so it can be binary searched.
    \end{itemize}
    
    \item \textbf{Templates}\\
    No need to create a separate test using templates, as we are only measuring build times in that case.\\
    The test case would also be to artificial.

    \item \textbf{Micro Benchmarks}\\
    In general create as many micro benchmarks as possible, as this is what we will be writing about in the report.
\end{itemize}

\subsubsection*{Other information from our supervisor}
Make sure to discuss the balance of the different aspects of flexibility vs performance vs complexity in the reports.

\end{document}
