\documentclass{article}

\begin{document}

\begin{center}
\subsection*{Supervisor meeting 10.02.2017}
\subsubsection*{With: Simon McCallum}
\end{center}

\bigskip

\subsubsection*{Intention of the meeting}
Getting some basic questions answered.


\subsubsection*{Questions to the supervisor}
\begin{itemize}
    \item 
    Is it ok to re-implement a lot of the C++ features, mainly to avoid long build times with heavy template usage.
\end{itemize}

\subsubsection*{Answers to our questions}
\begin{itemize}
    \item
    Yes, but show how templates are worse.
    \begin{itemize}
        \item
        Create a test case to show that templates might increase build times. 
        \item
        Can also refer to other implementors writing about the same subject. (Vittorio Romeo).
    \end{itemize}
    We can build a more skinned down version of our proposed ECS and one using templates, trying to stress the compiler.
    Even if the tests show that our perspective on build times is wrong, 
    we can still justify developing our systems because the stakeholder did not want much templating, 
    or also that our tests were not thorough enough as they were skinned down versions.
\end{itemize}

\subsubsection*{New tasks from our supervisor}
Start working with the the bachelor thesis, want a structure in place on the thesis.
Basically an outline of the thesis, with some work already in place.
Schedule the outline for the end of February.

\subsubsection*{Other information from our supervisor}


\end{document}