\documentclass{article}

\begin{document}

\begin{center}
\subsection*{Supervisor meeting 24.03.17}
\end{center}

\bigskip


\subsubsection*{Intention of the meeting}
Update supervisor on progress.

\subsubsection*{New tasks from our supervisor}
\begin{itemize}
    \item
    List in thesis that future work on the data access could be automated with a script or other tool.
    
    \item
    Discuss all trade offs within the thesis.

    \item
    Motivate all our choices based on the current situation and environment.

    \item 
    Motivate all the trade offs based on the future.\\
    Examples:
    \begin{itemize}
        \item
        If modules are added to the C++ standards, build times might get so good that template meta programming is a better option.

        \item
        Transactional memory might remove the need for lock free programming.

        \item
        ARM v8 has a sequentially consistent memory model.\\
        Relaxed atomics might not be necessary.
    \end{itemize}

    \item
    Have a section in thesis that documents what we know we are loosing with our methods.\\
    Examples:
    \begin{itemize}
        \item
        A lot of as-if optimizations.

        \item
        Inline functions. 
        
        \item
        "Type optimal" code based on template parameters.

        \item
        "Devirtualization".
    \end{itemize}

    \item
    Discuss the lack of familiarity when working with our system, does it impact productivity?

    \item
    Document all the changes of working processes.
\end{itemize}

\end{document}
