Test case

In general in these test cases we want to try as much as possible to make the performance measurements represent the specific case we are testing.
This means that we want to avoid using components that deals with code that we do not have full control over, like the Box2D and OpenGL code, focusing more on the actual test.





200+ different components
This case should display the possibility of having many differently functioning components. 

The test is performed by first creating 200 or more dummy components that does some simple task, just for testing purposes. 
We then place out several actors with the components in an otherwise empty world.
Might create a script which makes all off these components, as it would be a waste of time for us to manualy 

The test case is successful if the possibility of having that many components run properly at the same time over multiple actors at the same or greater performance of the NOX-Engine.





Multi-threading support
Show that the use of multi-threading in our implementation are actually giving a significant benefit in appropriate scenarios.

There setup for this is to create dummy components with waits inside their update functions, giving a consistent, but not a realistic scenario where multi-threading would improve performance.
Depending on how the multi threaded system works, we could do a lot of other specific tests to show the potential of the system.
For example the opt in idea for the multi threading could show off how effective it can be when used properly, and when it is ignored.

The test case is successful if there is a significant boost in performance 





Thread safe logging system
Show that the logging system has the possibility to function in a multi-threaded environment without any issues.

The test is conducted by creating a few components that run on different threads, and let them spam the logging system over a set period.

Successful if there aren't any crashes or errors over a substantial amount of time. 
This does not guarantee that it could not crash, but is a good indicator that everything is working at an acceptable level.




Memory usage
Compare the usage of RAM memory between the NOX-Engine and our system.
We want to avoid increasing the amount of memory used by as little as possible.
This is important because of the development towards the mobile platforms, which is lacking compared to the pc platform.

The measurement is easy, just check how much memory is in use.
However, we want to test a few different cases.
Like how much memory does a certain amount of empty actors use.
Is there a difference when having actors in such a way that the scenegraph has a very deep graph, or a lot of components in each actor.

Tested by comparing the memory used in the tests.





Compilation time
Should keep the compilation time as low as possible when building the engine.

There are a few ways to measure this.
First is to recompile the entire engine from scratch, but this is not a realistic scenario as this is not how it is done when actually developing in the engine.
The more realistic case is to see how much code needs to be recompiled when added additional components and such while developing games.

Tested by timing the time it takes to compile the engine. Could compare different compilers as well, besides the visual studio one.
