\documentclass{article}

\begin{document}

\begin{center}
\subsection*{Stakeholder meeting 21.02.17}
\end{center}

\bigskip


\subsubsection*{Intention of the meeting}
Discuss the design document.\\
Discuss test case document.

\subsubsection*{Questions to the stakeholder}
\begin{itemize}
    \item 
    Can we create some custom assert macros?

    \item
    Are any debug macros wanted within the ECS?

    \item
    What sort of tests are wanted, where are they wanted?

\end{itemize}


\subsubsection*{Answers to our questions}
\begin{itemize}
    \item
    Yes, create a NOX\_ASSERT forwarding to stdout.
    
    \item 
    It's ok, do whats needed.
    
    \item 
    General unit tests.\\
    Go for as much coverage as we want.

\end{itemize}

\subsubsection*{Feedback on design document}
Generally good, however some comments.
\begin{itemize}
    \item
    IComponent:
    \begin{itemize}
        \item
        Do not prefix with I, as an interface does not contain member data.

        \item
        Components can be only movable.
    \end{itemize}

    \item
    OperationTypes:
    \begin{itemize}
        \item
        Elaborate on wrapping lambdas, and rethink the description "opt-in type safety" as it is not really type safety.

        \item
        In general rethink how to explain the flexibility and opt-out solutions.
    \end{itemize}

    \item
    LogicEvent:
    \begin{itemize}
        \item
        Fix typo: in LogicEventOperation are use when components must respond to types (events).

        \item
        Rethink elaboration on LogicEventOperation.
    \end{itemize}

    \item
    TypeIdentifier:
    \begin{itemize}
        \item
        Think of doing a runtime check to ensure no collisions among the type identifiers.

        \item
        Would be nice to have a way of allowing checking for typo's during compile time when talking about type identifiers.
    \end{itemize}

    SmartHandle:
    \begin{itemize}
        \item
        Think of explaining the generations a bit better.
    \end{itemize}

    Lifecycle:
    \begin{itemize}
        \item
        Elaborate on the raw memory stage, explain properly that this is pooled memory, and that raw memory is either before operator new, or after operator delete.

        \item
        Rename inactive to awake.
    \end{itemize}

    Update Cycle:
    \begin{itemize}
        \item
        Distribute logic events before the update.

        \item
        Distribute events as long as events are sent. I.e. allow OnEvent functions to post new events.
    \end{itemize}
\end{itemize}

\subsubsection*{Feedback on Test case document}
Generally good, however some comments.
\begin{itemize}
    \item
    Make sure to use newest stable version of all the compilers.

    \item
    Ensure to that none of the busy waits are optimized away.

    Complete Compilation:
    \begin{itemize}
        \item
        All code that is pushed to the gitlabrepo is run on a server, meaning that compilation time is actually worth testing.
        
        \item
        All build folders are deleted, including cmake stuff (however we don't have to care about cmake stuff).

        \item
        Ensure that cmake caching is disabled when running the compilation tests.\\
        CMake caching is a global caching system, just deleting the files in the build folder wont remove it.

        \item
        Only look at single core compilation, as it just scales anyway when extra cores are added.

    \end{itemize}
\end{itemize}

\subsubsection*{Other information from our stakeholder}
All operations can be declared in the Component Base class.
Implementing the entityID assignment is done through constructor, base classes either inherit constructor or supply their own, sending the id up to the base.

\subsubsection*{Own thoughts}
Do we need special operations allowing for moving and swapping?

\end{document}
