\documentclass{article}

\begin{document}

\begin{center}
\subsection*{Stakeholder meeting 28.02.17}
\end{center}

\bigskip


\subsubsection*{Intention of the meeting}
Reporting on progress and clarify questions.


\subsubsection*{Questions to the stakeholder}
\begin{itemize}
    \item 
    Tools used when developing code, what sort of analysis are done? valgrind, cppcheck?

    \item
    Exception safety in ComponentCollection?

    \item
    Are runtime check for collisions really needed, what shall we do if we fail?
    
    \item 
    Standards in relation to creating library like interfaces, do we want to replicate the std interfaces?
    
    \item 
    Update ListenerManager to get the event types that are listened to.
    
    \item 
    Transporting the EntityManager, do we want pointers inn all the component functions, 
    or should they just have a pointer to the EntityManager.

    \item
    Should all functions be declared in the base component class and just left empty?\\
    They can still be nulled out if desired.

    \item
    Are asserts for lifecycles and duplicate components wanted in the ComponentCollection?

    \item
    Building for android. (Is it a lot of work?)

    \item
    Easy ways of quiting the application, events?
    
    \item
    Do you want a more different event system?\\
    Item based ECS Event system?
    \begin{itemize}
        \item
        Only trivial types?

        \item
        Can potentially do something akin to the meta information.
    \end{itemize}

\end{itemize}


\subsubsection*{Answers to our questions}
\begin{itemize}
    \item
    Nope, not continuously.

    \item
    Exception safety within ComponentCollection not needed.

    \item
    Just return a value indicating if there are any collisions.

    \item
    Follow nox standard, also when making "std" like facilities.

    \item
    Update ListenerManager to handle duplicate event types.
    Push this up to the nox engine repo.

    \item 
    Add the EntityManager as reference within the Components.

    \item
    Yes, all functions shall be declared, but empty.

    \item 
    Yes, add assert for invalid lifecycle states within ComponentCollection.

    \item
    Building and testing for android might be a bit of work, however do ensure that it builds for android.

    \item
    Currently the logic can't really stop the program.
    However our hack can still be used.

    \item 
    Sure. Its better to try and fail, than not trying.
\end{itemize}


\subsubsection*{New tasks from our stakeholder}
Create entity wrapper, holding the id, pointer to EntityManager etc.\\
Desired syntax:\\
entity.assignComponent(TypeIdentifier);\\
entity.hibernateComponent(TypeIdentifier); // Acts on component.\\
entity.hibernate(); // Acts on entire entity.\\
entity.getComponent();\\

\end{document}
