\documentclass{article}
\begin{document}
\begin{center}
\subsection*{Daily scrum meeting 01.02.2017}
\end{center}
\bigskip


\subsubsection*{What did we do yesterday?}

\noindent\textit{Trond Lohne}\\
\begin{itemize}
    \item
    Completed the rest of the meeting formats.

    \item
    Started looking into the NOX Engine. 
    Mainly the logging system.

    \item
    Started looking into different \LaTeX options for writing code etc.

\end{itemize}

\medskip

\noindent\textit{Per-Morten Straume}\\
\begin{itemize}
    \item
    Created a commit standard.

    \item
    Created an issue standard.

    \item
    Started working on the technical specification. 
    Mainly just trying to understand how the NOX Actor system works, 
    to understand functional requirements.

    \item
    Started looking into how we can do proper time tracking, 
    estimation and management without Jira.
\end{itemize}


\subsubsection*{What will we do today?}

\noindent\textit{Trond Lohne}\\
\begin{itemize}
    \item
    Start looking into the NOX Logic system. Understanding how it connects with the actor system.

    \item
    Start looking into different test cases we can make with the new ECS.

    \item
    Reading more research articles on ECS.
\end{itemize}

\medskip

\noindent\textit{Per-Morten Straume}\\
\begin{itemize}
    \item
    Start interacting with the bitbucket wiki. 
    Push some documents up there, like meeting notes etc.

    \item
    Continue working on the technical specification, 
    starting to write up the component, actor and world requirements.

    \item
    Look into parsing files from toggl and bitbucket to create a small estimation and work logging application.
\end{itemize}

\subsubsection*{Do we see any impediment that prevents us from meeting the sprint goal?}

\noindent\textit{Trond Lohne}\\
None

\medskip

\noindent\textit{Per-Morten Straume}\\
None


\newpage
\end{document}