\subsection{Components}
Components in this specification is described as a domain specific, decoupled and isolated
implementation of a certain behavior.

\ptparagraph{Initialization}
The initialization of a component can happen in two ways.
\begin{itemize}
    \item
    Through a json object.

    \item
    Directly in C++ code.
\end{itemize}

\ptparagraph{Data Access}
In regards to data access, components will have the current features.
These are just the "base" accesses, other features will be implemented when the "base" is extended.
\begin{itemize}
    \item
    Access to the current logic context of the application.

    \item
    Access to sibling components.
\end{itemize}

\ptparagraph{Queries}
Base components can be queried for the following information.
\begin{itemize}
    \item
    Information related to what type of object they are.

    \item
    Information related to whether or not they are in active state.
\end{itemize}

\ptparagraph{Lifecycle}
Components will be made aware of and can react to the following events in their lifecycle.
\begin{itemize}
    \item 
    A components own
    \begin{itemize}
        \item creation.
        \item activation.
        \item deactivation.
        \item destruction.
    \end{itemize}

    \item
    New sibling components attached and detached.

    \item
    New child actors being attached or detached from the owner.

    \item
    Events coming either sibling components, or other parts of the engine.

    \item
    Per frame updates.
\end{itemize}

\ptparagraph{Misc}
In addition to this, components will also support the following features.
\begin{itemize}
    \item
    Serialization into json objects.

    \item
    Safe casting operations.

    \item
    Support easy logging operations.\\
    i.e. Being able to log from inside a component.
\end{itemize}