\documentclass{article}
\usepackage{booktabs}
\usepackage[none]{hyphenat}
\usepackage{tabularx}

\newcommand*{\SignatureAndDate}[1]{
    \par\noindent\makebox[2.5in]{\hrulefill} \hfill\makebox[2.0in]{\hrulefill}
    \par\noindent\makebox[2.5in][r]{\textit{#1}}     \hfill\makebox[2.0in][r]{\textit{Date}}
}

\begin{document}
    \pagenumbering{gobble}
\section*{Group Rules}

\begin{enumerate}
    \item
        All time spent on the project will be tracked through toggl, with each entry given a proper headline indicating what sort of work that were done.
        When working on assigned issues/tasks the issue/task number is used to document in toggle, and also logged in Jira. 
        The logged work in Jira is an approximation, for example a bunch of small but frequently interrupted sessions can be summed into a total.
    
    \item
        A log will be written each work day, summing up progress and achievements for that day.
    
    \item 
        The expected amount of working hours per week is a minimum of 30 hours. 
        Monday through Friday. 
        If a group member has not contributed the required hours, he will work more to make up for it the week after.

    \item
        Academic disagreements are handled internally within the group at first, possibly including a supervisor or third party if no agreement can be reached.
    
    \item 
        Each day is started with a meeting, reporting on what tasks that will be completed that day, progress from the day before, what issues we are currently having. 
    
    \item 
        Meetings with the projects supervisor are scheduled to happen weekly or biweekly.
        All members of the group shall be present at said meetings.
    
    \item 
        Version control is done through git. Members are expected to commit and push often, documenting and securing their work.
        Commits shall happen at minimum once per working day.
             
    \item 
        Coding conventions shall be followed to the best of ones ability.

    \item
        Project lead will be the public representative of the group, and can therefore sign documents etc. on behalf of the group.

    \item
        Costs directly tied to the project will be split evenly among the group members.
\end{enumerate}

\subsection*{Consequences}
    All violations of these rules will be logged. 
    After three violations a written warning is given to the offending member, after the second warning a supervisor will be involved.
    A written warning will be signed by both the accusing and accused party, if any of the parties refuse to sign, a supervisor is contacted immediately.
    Deviation from these rules are allowed and wont have any consequences if it is cleared with the rest of the group first.

\subsection*{Contact Information}
\begin{tabularx}{\textwidth}{XXX}
    \toprule
    Name & Phone & Email \\
    \midrule
    Per-Morten Straume & 97186892 & p.m.straume@outlook.com \\
    Trond Lohne & 95919415 & trondlohne95@hotmail.no \\
    \bottomrule
\end{tabularx}

\subsection*{Signatures}
\bigskip
\SignatureAndDate{Trond Lohne}
\bigskip
\SignatureAndDate{Per-Morten Straume}


\end{document}



