\thesistitle{Multi-threaded Entity Component Systems for Game Engines}
\thesisshorttitle{NOX ECS} % use this if you have a very long title and want something shorter on the header pages
\thesisauthor{Per-Morten Straume}
\thesisauthorA{Trond Lohne}
\thesissupervisor{Mariusz Nowostawski}
%\thesissupervisorA{Simon McCallum} %TODO: Find out if we should list simon. %second supervisor

\nmtkeywords{ECS, Entity Component System, NOX, Game Engines, C++, Suttung}
\nmtdesc{The thesis examines the implementation of a multi-threaded entity component system.
The entity component system is built for the Norwegian game studio Suttung Digital, and
is based on requirements that are also applicable for other parts of the video game industry.
The thesis looks into implementation ideas for entity component systems, and
ways to run entity component systems in a multi-threaded environment.
The thesis also analyzes performance results, when benchmarked against Suttung's existing
actor system, and discusses some of the findings, and how it might be applicable to others.}

\nmtoppdragsgiver{Suttung Digital}
\nmtcontact{Magnus Bjerke Vik, magnus@suttungdigital.com, 98095297}

\thesisdate{\ntnubachelorthesisdate}
\useyear{16.05.2017}

\nmtappnumber{15} %number of appendixes
\nmtpagecount{77} %currently auto calculated but might be wrong

\thesistitleNOR{Multi-threaded Entity Component Systems for spillmotorer}
\nmtkeywordsNOR{ECS, Entity Component System, NOX, Spillmotorer, C++, Suttung}
\nmtdescNOR{Avhandlingen undersøker implementeringen av et multi-threaded entity component system.
Systemet er bygget for det norske spillstudiet Suttung Digital, og
er basert på krav som også gjelder for andre deler av spillbransjen.
Avhandlingen ser på implementeringsideer for entity component systems, og
måter å kjøre dem i et multi-threaded miljø.
I tillegg analyseres også ytelses resultater, hvor det sammenlignes med Suttungs eksisterende
actor system, samt diskuterer noen av funnene, og hvordan de kan være gjeldene for andre.}
