\section{Testing tools}
To ensure the legitimacy of the tests all the test cases will be run with different tools on different platforms.

\subsection{Compilers}
The tests will be built with the three most common compilers. 
\begin{itemize}

    \item
    MSVC
    
    \item
    Clang

    \item
    GCC

\end{itemize}


\subsection{Profilers}
The tests will be profiled with different profiling software based on what platform we are running on.

\subsubsection{Windows}
\ptparagraph{Visual Studio Profiler}
The visual studio profiler is a general purpose profiler with support for both instrumentation and sampling methods.
In this case the instrumentation functionality of the profiler will be used, to track statistics related to CPU Branch predictions, cache misses etc.

\ptparagraph{Very Sleepy}
Very Sleepy is a low overhead sampling profiler. 
Very Sleepy will be used for its function timing functionality, allowing us to inspect exclusive and inclusive function times with an application.

\subsubsection{Linux}
\ptparagraph{Perf}
Perf seems to be the "de facto" standard profiling tool on Linux, it uses a sampling based approach.
It allows for easy access to data related to branch prediction, cache misses etc. 

\ptparagraph{Callgrind}
Callgrind is part of the Valgrind toolset, and is an instrumentation profiler. 
In these tests it will mostly be used to recording inclusive and exclusive function times within the application.

\subsubsection{Comparison}
There are a limited number of multi platform profilers, meaning that comparing results between platforms might not be feasible.
However the intention of the project was never to measure differences between Windows and Linux, but between the different ECS implementations. 
For cross platform comparison we will use our own measurements of frame timing etc.