\subsection{Applying the Model}
We are going to use the standard scrum model with all of its various features, and also including some other features from some other development models as well.

These are the practices from XP and RUP that we use in our development model. 
\begin{itemize}
    \item Coding standard\\
    The coding standard is there to give a consistency throughout our code, making it easier for the team to read others code, and also come to an agreement on what is right and wrong ways to write certain bits of code.

    \item Collective code ownership\\
    Everyone should have as much insight in what happens in the entire project at all times.
    This is going to be solved with weekly code reviews, 
    explaining newly implemented code to the rest of the team.

    \item Simple design\\
    In every aspect of the project, we will have the mindset of
    trying to create a new functionality as simple as possible. 

    \item Project glossary\\
    In order to make the thesis easier to read through we want to include a project
    glossary to give an explanation/description on several abbreviations,
    terminologies, and other words which aren't necessarily that obvious.

    \item Software Architecture Description\\
    We want a proper laid out plan for the architecture of our entity component system. 
    This is tied up with one of our requirements to give Suttung a design document for
    the system and then have them approve it before we move into developing the actual system.

\end{itemize}

