\subsection{Milestones}
\subsubsection{Milestone 1: Specification}
\noindent\textbf{Technical Specification Document}\\
At the first milestone we will have a technical specification ready,
stating what functionality our ECS will provide, and what sort of performance
increases that they are interested in.

\noindenx\textbf{Performance Metrics Document}\\
In addition to the Technical Specification Document we will also have a document
describing the metrics that will be used when measuring performance on the different modules.

\noindent\textbf{Approved Test Case}\\
In addition to the approved design, we will at this point also have created a
relevant test case for our performance tests with the NOX Engine. 
This will also be approved by Suttung.

\subsubsection{Milestone 2: Iteration 1}
\noindent\textbf{Implemented Proposed ECS}\\
At this point in time the plan is to have our proposed entity component system
functionally implemented. Changes might come up throughout the rest of the project
however the API should be relatively set in stone at this point.
Optimization also falls under the category of implementation, as we will do 
performance measurements within the test case as well to guide our optimizations.

\noindent\textbf{Measured Proposed ECS}\\
The other part of this milestone is to have our ECS functioning properly within
the test case approved in the last milestone. 

\subsubsection{Milestone 3}
\noindent\textbf{Implemented Inheritance Based Test Case}\\
At this point in time we also want to have implemented the last of our "modules",
for the performance comparisons. It will be the same test cases as the other two
milestones, however this will be implemented with a more traditional inheritance focused
object oriented mindset.

\noindent\textbf{Performance Measurements}\\
At this stage in the project we will be doing some performance comparisons between
the different implementations.

\subsubsection{Milestone 4}
\noindent\textbf{Integrated ECS into NOX Engine}\\
At this point we will reach our final goal, which is to get the ECS integrated into the NOX Engine.
We will have done potentially needed refactoring and documentation.

\noindent\textbf{Gamejam with Suttung}\\
The plan is to have a gamejam with Suttung as a way of testing what they think of the new ECS.
It might also be interesting to do gamejam with other people without prior experience with the NOX Engine
to compare feedback on the two different systems.
