\documentclass[hidelinks]{article}
\setlength\parindent{0pt}

\usepackage{tabularx}



\begin{document}

\begin{titlepage}
    \centering
    {\scshape\LARGE NOX ECS 2: Scrum Plan 2 \par}
    \vfill
    {\large \date{}\par}
\end{titlepage}

\tableofcontents
\pagebreak

\section{Rationale}
The original scope of the assignment has grown to a larger extent, as a result of this a decision has been made to re-scope and re-plan the project.


\section{Goal}
While the old project goal was to implement two different ECS's with different strategies, we will now only implement one.
However moving over to only implementing one ECS allows us to do better testing
of our implementations, as well as allowing us to try some new ideas to improve performance like lock-free algorithms.

\section{Sprints}
The following sections contains the new sprints. The names of the sprints are kept the same, so the Gant chart in the original project plan can still be used.
After each sprint we will have a review of the sprint that has just passed, and after each second sprint we do a re-evaluation of our forward plan.

Sprint 11 is now gone, as it will be used for writing on the thesis instead.

The writing of the thesis is supposed to be done in a continuous manner, however since it will depend on the outline, 
direct tasks related to the thesis are not mentioned after sprint 4.


\subsection{Sprint 4}
\textbf{Time: 20.02-24.02}\\
\begin{tabularx}{\textwidth}{l >{\centering\arraybackslash}X}
\hline\noalign{\smallskip}
  Task                          & Testing Requirements   \\
\hline\noalign{\smallskip}
  \textbf{ECS}:                 &                        \\
  IComponent                    & Low                    \\
  OperationTypes                & Low                    \\
  MetaInformation               & Low                    \\ 
  SmartHandle                   & Med                    \\
  
  \textbf{EntityManager}:       &                        \\
  Assign Components             & High                   \\
  Get Components                & High                   \\

  \textbf{Logging}:             &                        \\
  Thread-safe Logging           & Med                    \\

  \textbf{Test Cases}:          &                        \\
  Compilation Time              & N/A                    \\
  Fast Spawning                 & N/A                    \\
  Numerous Unique Components    & N/A                    \\
  Memory Usage                  & N/A                    \\
  Multi-threading Support       & N/A                    \\

  \textbf{Thesis}:              &                        \\
  Outline Thesis                & N/A                    \\
  Write about test results      & N/A                    \\
\hline\noalign{\smallskip}
\end{tabularx}

\subsection{Sprint 5}
\textbf{Time: 27.02-03.03}\\
\begin{tabularx}{\textwidth}{l >{\centering\arraybackslash}X}
\hline\noalign{\smallskip}
  Task                              & Testing Requirements   \\
\hline\noalign{\smallskip}
  \textbf{ECS}:                     &                        \\
  Event System (Inheritance based)  & High                   \\
    
  \textbf{EntityManager}:           &                        \\
  Lifecycle                         & High                   \\
    
  \textbf{Test Cases}:              &                        \\
  Compilation time                  &  N/A                   \\    
  Fast Spawning                     &  N/A                   \\
  Numerous Unique Components        &  N/A                   \\            
  Memory Usage                      &  N/A                   \\
  Multi-threading support           &  N/A                   \\        
    
    \textbf{Thesis}:                &                        \\
\hline\noalign{\smallskip}
\end{tabularx}

\subsection{Sprint 6}
\textbf{Time: 06.03-10.03}\\
\begin{tabularx}{\textwidth}{l >{\centering\arraybackslash}X}
\hline\noalign{\smallskip}
  Task                              & Testing Requirements   \\
\hline\noalign{\smallskip}
  \textbf{Multi-threading}:         &                        \\
  Thread Pool                       & High                   \\
  Thread Safe Queue                 & High                   \\
  
  \textbf{Dependency Problem}:      &                        \\ 
  State Caching                     & High                   \\

  \textbf{Thesis}:                  &                        \\
\hline\noalign{\smallskip}
\end{tabularx}

\subsection{Sprint 7}
\textbf{Time: 13.03-17.03}\\
\begin{tabularx}{\textwidth}{l >{\centering\arraybackslash}X}
\hline\noalign{\smallskip}
  Task                              & Testing Requirements   \\
\hline\noalign{\smallskip}
  \textbf{Memory Efficiency}:       &                        \\
  Block Based Allocator             & High                   \\
  
  \textbf{Dependency Problem}:      &                        \\ 
  Direct Acyclic Graph (DAG)        & High                   \\

  \textbf{Thesis}:                  &                        \\
\hline\noalign{\smallskip}
\end{tabularx}

\subsection{Sprint 8}
\textbf{Time: 20.03-24.03}\\
Used as buffer to catch up before sprint 9 and 10.

\subsection{Sprint 9}
\textbf{Time: 27.03-31.03}\\
\begin{tabularx}{\textwidth}{l >{\centering\arraybackslash}X}
\hline\noalign{\smallskip}
  Task                                & Testing Requirements   \\
\hline\noalign{\smallskip}
  \textbf{Lock Free Multi-threading}: &                        \\
  Block Allocator                     & Very High              \\
  Queue                               & Very High              \\
  
  \textbf{Event System}:              &                        \\ 
  No Inheritance Based Implementation & High                   \\

  \textbf{Thesis}:                    &                        \\
\hline\noalign{\smallskip}
\end{tabularx}

\subsection{Sprint 10}
\textbf{Time: 03.04-07.04}\\
Used as a buffer or for additional tasks, like for example a test on Android devices.

\end{document}
