\documentclass{article}

\begin{document}

\begin{center}
\section*{Scrum Retrospective}
\subsection*{Sprint: 05}
\subsection*{01.03.17 - 08.03.17}
\end{center}
\bigskip

\subsection*{Time spent working on project}
\begin{itemize}
    \item
    Per-Morten: 26h

    \item
    Trond:      26h
\end{itemize}

\subsection*{What went wrong}
\subsubsection*{General}
\begin{itemize}
    \item
    Did not work enough.

    \item
    Miscalculation of time.

    \item
    Take research time into account when estimating.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Nothing outside of the general.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    "Spec" of the Event system was not entirely cleared at the start, leading to a lot of time trying to figure out how to do the event system, and how it should function.

    \item
    To granular issues. Hard to know which issue to work against.

    \item
    Json took up way more time than anticipated, and was a frustrating experience.
\end{itemize}

\subsection*{What went right}
\subsubsection*{General}
\begin{itemize}
    \item
    Felt time estimation were marginally better. This has to be checked.

    \item
    Review approach worked out okay. 
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Templating the trivial component class saved a lot of code duplication.

    \item
    Learning Valgrind took some time, however it was quite easy to learn.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    The interface for the event system was pretty straight forward to implement and seems clean.
\end{itemize}


\subsection*{What should we do differently}
\subsubsection*{General}
\begin{itemize}
    \item
    Start logging time against an overarching issue when doing research on a topic.
    Keep estimations and logging time against regular issues when actively working with them.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Start asking more questions when getting stuck.

    \item
    More consistent commits against issues.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    Make issues more high level, not to specific as it makes it hard to distinguish what exact issue I'm working on. 
\end{itemize}


\end{document}
