\documentclass{article}

\begin{document}

\begin{center}
\section*{Scrum Retrospective}
\subsection*{Sprint: 04}
\subsection*{20.02.17 - 28.02.17}
\end{center}
\bigskip

\subsection*{Time spent working on project}
\begin{itemize}
    \item
    Per-Morten: 47h

    \item
    Trond: 30h
\end{itemize}

\subsection*{What went wrong}
\subsubsection*{General}
\begin{itemize}
    \item
    Pull request and dependencies on the branches in those requests.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Miscalculated time.

    \item
    Mismanaging time. Should have dedicated more time.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    Miscalculated time.

    \item
    Dependencies on other team members. Mainly the google test.

    \item
    A lot of time waiting on response from stakeholder to clear up interface decisions.

    \item
    Memory Corruption bug took up more time than intended.
\end{itemize}

\subsection*{What went right}
\subsubsection*{Trond}
\begin{itemize}
    \item 
    I estimated the multi-threading logging task pretty close.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    The interface functioned quite well based on the design decision.

    \item
    Except from the memory bug, implementing the functionality was pretty straight forward.
\end{itemize}

\subsection*{What should we do differently}
\subsubsection*{General}
\begin{itemize}
    \item
    Start pull requests for the branches straight away, so that review can be done continuously. 
    
    \item
    Add a couple of hours extra to all estimations.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item
    Start taking the learning factor into account when estimating time.

    \item
    Use more time on the bachelor project.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    Don't expect tasks to be done in parallel, i.e. don't wait for google test examples, or reviews.

    \item
    Don't subdivide the issues to such a large extent.

\end{itemize}


\end{document}
