\documentclass{article}

\begin{document}

\begin{center}
\section*{Scrum Retrospective}
\subsection*{Sprint: 08}
\subsection*{20.03.17 - 27.03.17}
\end{center}
\bigskip

\subsection*{Time spent working on project}
\begin{itemize}
    \item
    Per-Morten: 35h 

    \item
    Trond:      38h
\end{itemize}

\subsection*{What went wrong}
\subsubsection*{General}
\begin{itemize}
    \item
    Some none productive days.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Some time was wasted trying to get certain tools to function properly.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    One day was entirely wasted as I was unable to focus.

    \item
    Some weird decisions in the Event class were made while I were still recovering from my sickness,
    which lead to some reworking of the Event and EventSystem class.
\end{itemize}

\subsection*{What went right}
\subsubsection*{General}
\begin{itemize}
    \item
    Finally retiring some of the old tasks that were just carry over from earlier sprints.\\
    This allowed us to refocus on the newer tasks without being burdened by the earlier tasks.\\
    Mainly the tasks that were removed were the testing tasks, which will be implemented if we get ahead of schedule.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Layered execution model worked out better than expected.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    The thread pool integration with the EntityManager went faster than expected.

    \item
    While it took some extra time, the linear allocators turned out quite fine.

    \item
    Because we put so many tasks on hold, I was able to start early on some tasks,
    leading to the lock-free allocator being functionally done, it only needs its documentation updated.
\end{itemize}


\subsection*{What should we do differently}
\subsubsection*{General}
\begin{itemize}
    \item
    We should have put more tasks on hold earlier, 
    or have a general rule that if a task has been carried over a certain number of times it should just be put on hold.
\end{itemize}

\subsubsection*{Trond}
\begin{itemize}
    \item 
    Nothing outside the general.
\end{itemize}

\subsubsection*{Per-Morten}
\begin{itemize}
    \item
    Think when a generalized solution is fine, rather than specialized one. 
    Some on the decisions made around the EventSystem were unnecessary, 
    leading to some unproductive and wasted time.
\end{itemize}


\end{document}
