\section{Criticism}
\label{sec:discussion_criticism}
There are several aspects of these findings that can be criticized.

\subsection{Single Compiler}
Due to time constraints we did not have time to run our tests on different compilers.
This means that we did not get to inspect how different compilers might optimize our code differently.

\subsection{Single Platform}
We originally planned to test on both Windows and Linux, while also testing on both our computers to
try with different hardware. However, time only allowed us to test on Linux, and with only one computer.
We are uncertain as to how much difference it would actually be if we also tested on other computers.

\subsection{Counter Test Cases}
Due to lack of time we did not have the option to write different systems to test.
For example, it would have been interesting to create a template based entity component system,
to measure against.

\subsection{Different Functionality}
A major flaw within the benchmark tests is that the two different systems does not offer all the same functionality.
We argue that this does not to such a degree influence the timing tests, but rather highlights the different approaches
between the development of the two systems.
Both system were used in their intended fashion, and the use of NOX ECS was not entirely optimal.
In the memory tests the extra functionality should be taken into account, as parts of the extra memory usage
comes from this functionality.
The difference in memory is rather large, and we believe that even when the extra functionality is implemented,
the NOX ECS will use less memory than the NOX Actor system.

\subsection{No Overarching Representative Test Case}
Due to time constraints we were unable to create a realistic test case that combined the different behavior
of the test cases.
The optimal situation would be to create a small game which could show the differences between the two systems.

\subsection{Repeated Tests}
Due to the issues that were discovered late in the testing phase, we did not have time to repeat the tests
as much as desired.
This is mainly applicable to the tests between NOX ECS and the NOX Actor system, but here the differences
between the performance is quite clear.
The numerous unique components internal test were repeated ten more times, and the differences between
the results were relatively consistent. However, even more repetition is desired here to give more reliable numbers.
